\begin{acknowledgements}
\noindent My sincere gratitude towards my thesis supervisor, Dr. Prasenjit Ghosh for inculcating scientific temperament and providing unwavering support. It has been a pleasure working and learning under his guidance.
I relay by kind acknowledgements to my  Research Advisory Committee (RAC) members: Prof. Arnab Mukherjee and Prof. Nirmalya Ballav for their mindful suggestions throughout my research tenure. I am equally grateful to my collaborators: Dr. Ali Hassanali and Ivan Girotto for the riveting discussions and their consideration towards my research.  

\noindent I render my deepest appreciation to our Director, Prof. Jayant B. Udgaonkar, and other staff members for providing the infrastructure and logistics to perform cutting edge research. I thank Indian Institute of Science Education and Research Pune (IISER Pune) for providing in-house computational facilities and International Centre for Theoretical Physics (ICTP) for providing access to Marconi, Cineca clusters, Italy. I acknowledge PRACE for awarding access to MareNostrum Supercomputer at Barcelona, Spain through PRACE proposal no. 2019215139. I also acknowledge the funding from the National Supercomputing Mission (NSM), Department of Science and Technology, India, through grant nos. DST/NSM/R$\&$D\_HPC\_Applications/2021/03.36, \\ DST/NSM/R\&D\_HPC\_Applications/2021/03.36.02 and \\ DST/NSM/R\&D\_HPC\_Applications/2021/03.36.03. This also includes providing computing resources of `PARAM Brahma’ at IISER Pune and `PARAM-Utkarsh' at CDAC-Bangalore, which is implemented by C-DAC and supported by the Ministry of Electronics and Information Technology (MeitY) and Department of Science and Technology (DST), Government of India. Additionally, I would like to thank the Center for Computational Materials Science, Institute for Materials Research, Tohoku University, Japan for providing me access to the MASAMUNE supercomputer.

\noindent On a personal level, I will always be grateful to my family, friends, lab mates and football. 
\end{acknowledgements}

